graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-05-08 paper/paper.Rmd
correct figure widths (fig2-4, pane E)

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: 30 April 2020
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---

@@

#plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
mtext(text = "(b) relationship matrix", side=1, line=3, at=0.075, adj=0.5, cex=1.75)

@@

#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)),
sub = "(e) Simulated expression data (log scale)", cex.sub = 1.75,
xlim = c(-0.5, 1.5))
```

>>>>

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    keep_tex: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: 30 April 2020
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---

@@

op <- par(mfrow=c(2,2), mar=c(4,4,4,1), oma=c(0.5,0.5,0.5,0))
#plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
mtext(text = "(b) relationship matrix", side=1, line=3, at=0.075, adj=0.5, cex=1.75)

@@

op <- par(mfrow=c(1,1), mar=c(4,4,4,1), oma=c(0.5,0.5,0.5,0))
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3, at=0.075, adj=0.5, cex=1.75)
par(op)
```
